Notes: New gaugings in 3d from three-form

### 2023-05-30 Notes_3dH3.tex
Small changes before pulling Emanuel's updates.

>>>>

\section{Mass matrices}
\subsection{Vector fields}
\begin{equation}
  M_{(1)}{}^{\bar M}{}_{\bar N} = X^{\bar M\bar P}\left(\eta_{\bar P\bar N} + \M_{\bar P\bar N}\right).
\end{equation}

\subsection{Scalar fields}
We define the scalars using coset representative ${\cal V}_{\bar M}{}^{\bar N}\in\E_{8(8)}/\SO(16)$:
\begin{equation}
  {\cal V} = \exp\left(\Phi^{\bar A}\,T_{\bar A}\right),
\end{equation}
with $\left(T_{\bar A}\right)_{\bar M}{}^{\bar K}$ the non-compact generators of $\E_{8(8)}$. Let $\Delta_{\bar M\bar N}$ be a matrix such that these generators satisfy
\begin{equation}
  \left(T_{\bar A}\right)_{[\bar M}{}^{\bar K}\Delta_{\bar N]\bar K} = 0.
\end{equation}
We then construct the scalar matrix from coset representatives:
\begin{equation}
  \M_{\bar M\bar N} = {\cal V}_{\bar M}{}^{\bar P}{\cal V}_{\bar N}{}^{\bar Q}\,\Delta_{\bar P\bar Q}.
\end{equation}

Then, the scalar fields mass matrix (at the scalar origin) is
\begin{equation}
  M_{(0)\,\bar A\bar B}^{2} = {\cal P}_{\bar A}{}^{\bar M\bar N}{\cal P}_{\bar B}{}^{\bar P\bar Q}\left(\frac{1}{7}\,X_{\bar M\bar P}X_{\bar N\bar Q}+X_{\bar M\bar K}\left(\frac{1}{7}\,\Delta^{\bar K\bar L}+\eta^{\bar K\bar L}\,X_{\bar L\bar P}\,\Delta_{\bar N\bar Q}\right)\right).
\end{equation}
The mass matrix for a vacuum away from the scalar origin is given by the same formula, where all occurences of embedding tensor should be modified to the ``dressed'' embedding tensor.
